% A summary of learned skills (~0.5 page)

\section{Learned Skills}

During this two semester project group,
I have learned a lot in all aspects. 

% Scrum
We used Scrum to manage our team,
I have therefore gathered experience with Scrum, 
e.g. How to be a Scrum master to organize a team, 
how to manage weekly tasks with a board, 
and what to do in meetings. 
Also, the most important thing is how to work as a team, 
since I usually worked alone previously. 

% coding
I have also improved my coding style in this project. 
Thanks to the linter, 
I wrote more readable code and never forgot to add comments to functions, 
which make it easier for others and me later to understand.

% git
I have also formed good habits in git, 
committing frequently and with meaningful comments. 
I practiced git functions such as creating new branch, merging, rebasing, 
and also how to handle merge conflicts.
Additionally, I have learned how to set up CI/CD in Github from my teammates, 
which simplified our deployment.

% VM
This is my first time working with server on a virtual machine
with nginx, REST and docker. 
I think this experience can be applied on many other projects. 

% dbpeida
I got my first insight into knowledge graph in this project group
and knew how SPARQL query is written. 

% NLP
The last but not least,
I learned much about natural language processing in practice, 
including encoder and decoder, tokenizer and model training. 
I had some experience in building our own dataset for a NLP model. 
Beyond neutral network, I also became acquainted with transformer,
a much powerful machine learning model for NLP. 